Water Management

### 2020-02-28 Paper/paper.tex
use->utility

\begin{equation}
	mean = exp(\mu+\frac{\sigma^2}{2}) \label{eq:rainfall}
\end{equation} 
Both distributions are visualized in \ref{fig:rain-distributions}.
\begin{figure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1\textwidth]{figures/rainfall-default.eps}
		\caption{$\mu=0, \sigma^2=1$}
		\label{fig:rainfall-default}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\textwidth]{figures/rainfall-more-volatile.eps}
		\caption{$\mu=-1.5, \sigma^2=4$}
		\label{fig:rainfall-changed}
	\end{subfigure}
	\caption{Different Rainfall Distributions}
	\label{fig:rain-distributions}
\end{figure}
\newpage
\begin{figure}[ht]
	\includegraphics[width=1\textwidth]{figures/aggregated-use-rainfall-default.eps}
	\caption{Aggregated Use for lognormal distributed rainfall $(\mu=0, \sigma^2=1)$}
	\label{fig:aggregated-use-rainfall-default}
\end{figure}
\begin{figure}[ht]
\includegraphics[width=1\textwidth]{figures/aggregated-use-rainfall-more-volatile.eps}
\caption{Aggregated Use for lognormal distributed rainfall $(\mu=-1.5, \sigma^2=4)$}
\label{fig:aggregated-use-rainfall-more-volatile}
\end{figure}

The following figures demonstrate the effect of the changed volatility. They show the lognormal rainfalls with the original volatility (\ref{fig:aggregated-use-rainfall-default}), and with the increased volatility (\ref{fig:aggregated-use-rainfall-more-volatile}) over 100 periods. 
When comparing both visualizations, we see that more extreme rainfalls significantly affect the water level of the reservoir: there are longer periods with a rather low amount of water in the reservoir, but some periods where the reservoir reaches it's capacity limit. 
%When comparing both visualizations,it is noticeable that more volatile rainfall leads to much higher peaks of rain in combination with reduced number of periods with a decent amount of rain. 
%As a consequence the water level in the reservoir fluctuates much more leading to periods with almost no water in the reservoir. 
In the periods with only low precipitation, the farmers use almost no water for irrigation. 
The aggregated utility of farmers and recreational users drops significantly. 
Since the reservoir is capped at an amount of 7, the high peaks of the rainfalls can only partially be used in following (potentially dryer) periods. 
Generally speaking, one can say that a more volatile rain distribution leads to a lower average water level in the reservoir with lower amounts of water to be used for irrigation.
This effect is reflected in the aggregated utility as well. 
The utility of more volatile rainfall is much lower compared to rainfall parameterized with $\mu=0$ and $\sigma^2=1$. 
Since the mean stays the same in the two cases considered, the value function does not change.

>>>>

\begin{equation}
	mean = exp(\mu+\frac{\sigma^2}{2}) \label{eq:rainfall}
\end{equation}

Both distributions are visualized in \ref{fig:rain-distributions}.

\begin{figure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1\textwidth]{figures/rainfall-default.eps}
		\caption{$\mu=0, \sigma^2=1$}
		\label{fig:rainfall-default}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\textwidth]{figures/rainfall-more-volatile.eps}
		\caption{$\mu=-1.5, \sigma^2=4$}
		\label{fig:rainfall-changed}
	\end{subfigure}
	\caption{Different Rainfall Distributions}
	\label{fig:rain-distributions}
\end{figure}

%TODO in figure+code use durch utility ersetzen
\begin{figure}[ht]
	\begin{subfigure}{\textwidth}

	\includegraphics[width=1\textwidth]{figures/aggregated-utility-rainfall-default.eps}
	\caption{Lognormal distributed Rainfalls with $\mu=0$ and $\sigma=1$}
	\label{fig:aggregated-utility-rainfall-default}

	\end{subfigure}
	\newline
	\begin{subfigure}{\textwidth}

	\includegraphics[width=1\textwidth]{figures/aggregated-utility-rainfall-more-volatile.eps}
	\caption{Lognormal distributed Rainfalls with $\mu=-1.5$ and $\sigma=2$}
	\label{fig:aggregated-utility-rainfall-more-volatile}

	\end{subfigure}
	\caption{Effects of more volatile Rainfalls over Time}
	\label{fig:aggregated-utilities-rainfall}
\end{figure}

The graphs in \ref{fig:aggregated-utilities-rainfall} demonstrate the effect of the changed volatility. They compare the lognormal rainfalls with the original volatility, and with the increased volatility over 100 periods. 
When comparing both visualizations, we see that more extreme rainfalls significantly affect the water level of the reservoir: there longer periods with a rather low amount of water in the reservoir, but some periods where the reservoir reaches it's capacity limit. 
%When comparing both visualizations,it is noticeable that more volatile rainfall leads to much higher peaks of rain in combination with reduced number of periods with a decent amount of rain. 
%As a consequence the water level in the reservoir fluctuates much more leading to periods with almost no water in the reservoir. 
In the periods with only low precipitation, the farmers use almost no water for irrigation. 
The aggregated utility of farmers and recreational users drops significantly. 
Since the reservoir is capped at an amount of 7, the high peaks of the rainfalls can only partially be used in following (potentially dryer) periods. 
Generally speaking, one can say that a more volatile rain distribution leads to a lower average water level in the reservoir with lower amounts of water to be used for irrigation.
This effect is reflected in the aggregated utility as well. 
The utility of more volatile rainfall is much lower compared to rainfall parameterized with $\mu=0$ and $\sigma^2=1$. 
Since the mean stays the same in the two cases considered, the value function does not change.
